---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(gluestick)
```

# gluestick

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![R-CMD-check](https://github.com/coolbutuseless/gluestick/workflows/R-CMD-check/badge.svg)](https://github.com/coolbutuseless/gluestick/actions)
<!-- badges: end -->

The goal of the `gluestick` package is to provide a home for a single, simple function 
(also named `gluestick`).

This `gluestick()` function is meant to be an almost drop-in replacement 
for 99.9% of the reasons I use the amazing [`glue`](https://cran.r-project.org/package=glue) package.

The idea is that you would just steal the function out of this package and use 
it in your own package in order to avoid having [`glue`](https://cran.r-project.org/package=glue)
as a dependency.

## Benefits

* Single function
* No dependencies
* No C code
* Vanilla base R code (easy to hack upon)

## Limitations

* There is no special handling when delimiters are repeated.  This differs from
  `glue` where doubling the delimiter escpaes it.
* No support for glue's idea of data transformers
* Far fewer sanity checks than glue

## Installation

You can install from [GitHub](https://github.com/coolbutuseless/gluestick) with:

``` r
# install.package('remotes')
remotes::install_github('coolbutuseless/gluestick')
```

In reality, I can't see anyone actually wanting to install/use this package 
in preference to the glue package.

What I envisage is that if you want something "glue-like" to include in your 
own work, you can just steal the `gluestick()` function out of this package
and include it in your own package.

## Basic Usage

```{r example}
library(gluestick)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# By default, `src` data is the calling environment
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
name <- 'Mike'
gluestick("Hello {name}")

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# R code will be evaluated
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
gluestick("Hello {name}. Score = {1 + 2}")

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Can pass in a list, data.frame, environment etc as the data source to 
# override the default
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
gluestick("Hello {name}", src = list(name = '#RStats'))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Delimiters are user-definable
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
gluestick("Hello ~~!name]]?", open = "~~!", close = "]]?")
```


## Do not evaulate expressions - treat them as referencing named variables only

In some circumstances it might be wise to assume that the expressions ren't actually
R code, but only refer to names of variables in the data source.  This might 
be useful when evaluating format strings input by an untrusted user.

If `eval=FALSE` is set, then expressions will be treated as variable names, and
`mget()` will be used to fetch them from the data source, and no code 
evaluation will occur.


```{r error = TRUE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# This will work, as 'name' is a variable in the data `src` (i.e. the calling environment)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
gluestick("hello {name}", eval = FALSE)


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# This won't work as the code is not evaulated, and there is no variable 
# named `2 * 2` in the `src` data
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
gluestick("hello {2 * 2}", src = list(name = 'mike'), eval = FALSE)
```






## Related Software

* Functionality is heavily modelled on [`glue`](https://cran.r-project.org/package=glue)


## Acknowledgements

* R Core for developing and maintaining the language.
* CRAN maintainers, for patiently shepherding packages onto CRAN and maintaining
  the repository
